---
title: "Group 48 UCSB domestic grad enrollment"
author: "Shuying Yu and Kiera Matiska"
date: "11/15/2021"
output: html_document
---

```{r setup, include = TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Attach packages
library(tidyverse)
library(here)
```


# Read in the data

Use the `read_csv()` fuction and the `here` package to read in ucsb_grad_data.csv

```{r}
#Read in data
ucsb_grad <- read_csv(here("data", "ucsb_grad_data.csv"))
```

# Visualize Data

Create a column graph showing the change in domestic enrollment (y-axis: `domestic_enrollment`) by year from 2008 - 2019 (x-axis: `year_abbr`)

```{r}
#Column plot
ggplot(data = ucsb_grad,
       aes(x = year_abbr, y = domestic_enrollment)) +
  
  #Define column plot
  #Color by ethnicity
  #Convert column counts to proportions
  geom_col(aes(fill = ethnicity),
           position = "fill") + 
  
  #Change x-axis and y-axis labels
  #Add title
  #Change legend title
  labs(x = "Year \n(Abbreviated)",  
       y = "Domestic Graduate Enrollment at UCSB (%)", 
       title = "Demographics of UCSB Domestic Graduate Student \nEnrollment from 2008 - 2019",
       fill = "Ethnicity") + 
  
  #Change theme
  theme_minimal() +
  
  #Center title
  theme(plot.title = element_text(hjust = 0.5))
```
**Figure 1.** Demographics of UCSB Domestic Graduate Student Enrollment by Year. From 2008 to 2019, white students dominated the enrollment numbers with upwards of 50% enrolled each year. All other races and ethnicities listed make up a much smaller percentage of the total enrollment each year. Data source: UCSB, Campus Profiles (2008-2019).

**Data citation:** University of California, Santa Barbara, Office of Budget and Planning. Institutional Research, Planning, & Assessment, Campus Profiles (Years: 2008-2019). The Regents of the University of California. https://bap.ucsb.edu/institutional-research/campus-profiles. 
