---
title: "Group 48 UCSB domestic grad enrollment"
author: "Shuying Yu and Kiera Matiska"
date: "11/15/2021"
output: html_document
---

```{r setup, include = TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Attach packages
library(tidyverse)
library(here)
```


# Read in the data

Use the `read_csv()` fuction and the `here` package to read in ucsb_grad_data.csv

```{r}
#Read in data
ucsb_grad <- read_csv(here("data", "ucsb_grad_data.csv"))
```

# Visualize Data

Create a column graph showing the change in domestic enrollment (y-axis: `domestic_enrollment`) by year from 2008 - 2019 (x-axis: `year_abbr`)

```{r}
# Column plot
ggplot(data = ucsb_grad,
       aes(x = year_abbr, y = domestic_enrollment)) +
  geom_col(aes(fill = ethnicity), # #Define column and color by ethnicity
           position = "fill") + # Convert column counts to proportions
  labs(x = "Year \n(Abbreviated)",  # Change x-axis label
       y = "Domestic Graduate Enrollment at UCSB (%)", # Change y-axis label
       title = "Domestic Graduate Enrollment Demographics by Year") + # Add Title
  theme_minimal() # Changed theme to minimal
```
**Figure 1.** Domestic Graduate Enrollment Demographics by Year. From 2008 to 2019, white students dominated the enrollment numbers with upwards of 50% enrolled each year. All other races and ethnicities listed make up a much smaller percentage of the enrollment each year. 
